{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-10-20 sftrends_manu.tex
author updates

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Tue Oct 18 17:52:14 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

The Delta region is of particular interest for understanding historical patterns and potential trajectories of water quality response to nutrient inputs into the Bay.  The Delta is a mosaic of linked channels or tracts that receive, process, and transport inflows from the Sacramento and San Joaquin rivers to the lower Bay.  Quantitative descriptions of nutrient dynamics in the Delta are complicated by the numerous sources that contribute input loads.  Sources are not limited to the watershed, such that local inputs from wastewater and internal loading from sediment processes also represent important contributions.  Seasonal and annual variation in the delivery of water inflows, including water exports directly from the Delta, have complicated the interpretation of trends in nutrient concentrations. Accordingly, quantitative descriptions of nutrient dynamics in the Delta must explicitly account for the effects of flow changes to better understand variation both within the Delta and potential mechanisms of downstream tranport.

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$, Phil Trowbridge$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Wed Oct 19 16:59:28 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

The Delta region is of particular interest for understanding historical patterns and potential trajectories of water quality in response to nutrient inputs into the Bay.  The Delta is a mosaic of linked channels or tracts that receive, process, and transport inflows from the Sacramento and San Joaquin rivers.  Quantitative descriptions of nutrient dynamics in the Delta are complicated by the numerous sources that contribute input loads.  Sources are not limited to the watershed, such that nutrient concentrations can also originate from local wastewater inputs and internal loading from sediment processes.  Seasonal and annual variation in the delivery of water inflows, including water exports directly from the Delta, have further complicated the interpretation of trends in nutrient concentrations. A comprehensive evaluation of nutrient dynamics using mass-balance models showed that

Accordingly, quantitative descriptions of nutrient dynamics in the Delta must explicitly account for the effects of flow changes to better understand variation both within the Delta and potential mechanisms of downstream tranport.
